### 2019-05-16 manuscript/response.tex

check % TODO

\begin{quote}
Line 465-469: This sentence was a bit difficult to grasp during my first reading of it.
I get the point, but I think the authors might consider revising it for clarity.
\end{quote}

Rephrased. % TODO

\begin{quote}
Line 476-480: The type I error issues reported by Rabosky and Goldberg (2015) are, in my view, fairly universal.
So, I think it is safe to say that MuSSE ``does suffer'' issues of model misspecification/type I error.
Also, it is worth noting that there are several implementations that already include hidden states in a MuSSE model, most notably the HORRIBLY named SecSSE model, as well as the models used in a recent empirical paper on diatoms by Nakov et al (which I've seen on bioRxiv, though might be published by now).
\end{quote}

Yes, and indeed this has already been shown.
We fixed the text and added a reference.

### 2019-05-16 manuscript/discussion.tex
fixed up small points from reviewer 3

%B: Rosana, read this carefully, please! I think it may need review:
%B: I changed nothing here, except: (1) a citealt<-citet to avoid double parentheses. (2) sp. disscussed -> discussed, (3) "If that is the case ON a system" -> "... IN a system"? (4) "hight type I errors" -> high, type I errors [comma], (5) line break in penultimate sentence.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as discussed in \citealt{rabosky_2010, beaulieu_2015}), but also a problem of inadequate ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focal trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case in a study system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process.  % E: I would say not necessarily.  There could be other non-trait weirdnesses.
When considering a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE might also suffer from high type I errors, considering more heterogeneity using a hidden state model on top of the multi-state diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule, rather than the exception. 
Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.

>>>>

%B: Rosana, read this carefully, please! I think it may need review:
%B: I changed nothing here, except: (1) a citealt<-citet to avoid double parentheses. (2) sp. disscussed -> discussed, (3) "If that is the case ON a system" -> "... IN a system"? (4) "hight type I errors" -> high, type I errors [comma], (5) line break in penultimate sentence.
Estimating rates of trait linked diversification models is not only a problem of difficult parametric inference (as discussed in \citealt{rabosky_2010, beaulieu_2015}), but also a problem of inadequate ``*SSE'' model specification that can result in misleading inferences when the presence of a second trait has a complex interaction with the focal trait first used to model diversification. 
We presented a roadmap with a series of analyses that can identify whether unknown or unobservable traits are worth pursuing. 
In this roadmap, we have proposed fitting HiSSE models that have effectively shown that some binary states associated with diversification under BiSSE analyses are actually not different in net diversification terms, and instead a hidden state is linked to differences in the diversification rate \citep{beaulieu_2016}.  
If that is the case in a study system, raising the question of the identity of the hidden state should be considered as the next step in the modeling process.  % E: I would say not necessarily.  There could be other non-trait weirdnesses.
When considering a second candidate trait, one can model the complex interactions via a MuSSE model, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood. 
Since MuSSE can also falsely associate traits with diversification \citep{fitzjohn_2012}, considering more heterogeneity using a hidden state model on top of the multi-state diversification model is necessary to adequately infer the effect of the complex interactions in the speciation and extinction process.
% R- new lines
Investigating the process of diversification linked to traits can be done via thorough statistical inferences that carefully evaluate multiple evolutionary histories. 
Background heterogeneity in lineage of diversification is the rule, rather than the exception. 
Inferences that question whether other complex trait interactions are hidden in this background heterogeneity are necessary because they critically contribute to the reconstruction and understanding of diversification.
